%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Work Experience}
\cvsection{Relevant Work Experience}

\newcommand{\toronto}{Toronto, Canada}
\newcommand{\winnipeg}{Winnipeg, Canada}
\newcommand{\weingarten}{Weingarten, Germany}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Loss Prevention Consultant/Engineer} % Job title
    {FM Global} % Organization
    {\toronto} % Location
    {Apr 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assessed \& identified property \& business interruption risks at client facilities.}
        \item {Consulted, fcoached \& sold clients on performing property risk improvements at their site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Analyst Student (part time)} % Job title
    {eHealth Innovation @ University Health Network} % Organization
    {\toronto} % Location
    {Sep 2017 - Sep 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed, cleaned, and processed telehealth smartphone app usage data.}
        \item {Tools: Python (numpy, pandas), Google Analytics, Excel/Power BI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Human Factors Student Intern} % Job title
    {Healthcare Human Factors @ University Health Network} % Organization
    {\toronto} % Location
    {Jan 2017 - Apr 2017, Jan 2018 - Apr 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitated \$0.5M, 60+ participant, multi-device usability evaluation (in the United States) under very tight deadlines.}
        \item {Evaluated medical device usability, designing \& proposing changes to improve user interface \& user experience.}
        \item {Created database to help track and identify eligible human factors study participants.}
        \item {Tools: MySQL, HTML/CSS/Javascript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant (CSC444: Software Engineering I)} % Job title
    {University of Toronto} % Organization
    {\toronto} % Location
    {Sep 2017 - Dec 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored students in using agile software engineering principles to create a functional web service.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Electrical Engineer-in-Training (temp)} % Job title
    {Nova 3 Consulting Engineers} % Organization
    {\winnipeg} % Location
    {May 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered fire/emergency, HVAC control, lighting \& power distribution systems for healthcare \& other occupancies.}
        \item {Designed \& drafted electrical plans total >\$150k in billables.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Freelance Research Assistant} % Job title
	{University of Manitoba} % Organization
	{\winnipeg} % Location
	{May 2014 - Jun 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented iOS app for monitoring wounds/bedsores. \cite{Baril2015}}
			\item {Mapped \& analyzed the brain connectivity networks of epileptic patients during various sleep stages. \cite{Baghbani2015}}
			\item {Tools: Objective-C, XCode, MATLAB}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Visiting Scholar} % Job title
	{Ravensburg-Weingarten Uni. of Applied Science} % Organization
	{\weingarten} % Location
	{May 2013 - Aug 2013} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Repaired the control system (C++) of a remote-controlled rover as part of an international cross-disciplinary team.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Electronics Engineering Intern} % Job title
	{Parker Hannifin (Electronics Control Division)} % Organization
	{\winnipeg} % Location
	{Sep 2011 - Aug 2012} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Oversaw creation \& verification of production prototypes, including multiple \$40k custom training interfaces.}
			\item {Performed design verification testing including electromagnetic compatibility, electrostatic discharge, alarm sound intensity, thermal \& load testing.}
			\item {Creating database to track prototypes and test equipment.}
			\item {Tools: MS SQL, MS Access}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{NSERC Undergraduate Research Assistant} % Job title
	{University of Manitoba} % Organization
	{\winnipeg} % Location
	{May 2011 - Aug 2011} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Analyzed time-series data producing peer-reviewed paper.}
			%\item {Investigated alternate locations for recording swallowing sounds.}
			\item {Tools: MATLAB, signal processing toolbox (pwelch, spectrogram), standard I/O \& plot libraries.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Junior Automated Rating Analyst} % Job title
	{Federated Insurance} % Organization
	{\winnipeg} % Location
	{Summers 2008 - Aug 2010} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Maintained underwriting algorithms ensuring pricing accuracy \& regulatory compliance. }
			\item {Trained \& mentored junior summer hires.}
		\end{cvitems}
		%\begin{cvsubentries}
		%  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
		%  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
		%\end{cvsubentries}
	}

%---------------------------------------------------------
\end{cventries}
