%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
	{University Affairs Representative (Elected)} % Affiliation/role
	{Biomedical Engineering Student Association (University of Toronto)} % Organization/group
	{\toronto} % Location
	{Sep 2017 - Sep 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {Represented association at various university/departmental/union meetings.}
			\item {Planned \& facilitated annual general meeting.}
			\item {Piloted program to improve communication to student body.}
		\end{cvitems}
}

%---------------------------------------------------------
  \cventry
	{Facilitator} % Affiliation/role
	{Discovery Program (University of Toronto)} % Organization/group
	{\toronto} % Location
	{2016, 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {Facilitated CAD \& 3D printing design workshop activities designed to introduce high school students to biomedical engineering research.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Short-Term Volunteer} % Job title
	{Youth with a Mission} % Organization
	{UK, Italy, Greece, \& Central Asia} % Location
	{Jun 2015 - Dec 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Supported local relief work for Syrian refugees \& local disadvantaged people groups.}
			\item {Taught English as a foreign language to local students.}
			\item {Modernized local accounting and budgeting system.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Executive \& Founding Member} % Affiliation/role
	{University of Manitoba Biomedical Engineering Society} % Organization/group
	{\toronto} % Location
	{2012 - 2014} % Date(s)
	{
		\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {Established strategic direction including drafting group constitution.}
			\item {Organized and facilitated annual outreach event to promote biomedical engineering to 1st year students.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
